Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Add TODO regarding coverage of attacks
Increase image size
Add an em of space after the abstract.
Pret-a-voter beginnings.

  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.

\end{onecolabstract}
]

@@

\pv\ aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/preta.pdf}
	\caption{\pv{} ballot}
	\label{fig:preta}
\end{figure}

@@

>>>>

  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.
    \vspace{1em}
\end{onecolabstract}
]

@@

\pv\ also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

The paper ballot form in \pv\ consists of two separable sides. The left-hand side lists the candidates in permuted order. A mark on the right-hand side in an initially empty slot adjacent to a candidate indicates a vote for that candidate. In addition to the recorded vote, the right-hand side also includes the so-called ``onion'', an encryption of the ballot's particular candidate permutation. See Figure \ref{fig:preta} for a depiction of the ballot form.

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/preta.pdf}
	\caption{\pv{} ballot}
	\label{fig:preta}
\end{figure}

\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations.}

Upon arriving at the polling place, a voter receives one or more ballots. She chooses one of her ballots forms at random and privately marks her vote on the right-hand side. She detaches her cast vote from the corresponding candidate list on the left-hand side, which is subsequently destroyed. Her cast vote is scanned into and recorded by the system, which prints a digital signature on the now recorded ballot to constitute a receipt. The voter retains this receipt to later verify that her vote appears correctly in the tally.

The voter can optionally request an audit of her other ballot(s) to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side. Once audited, a ballot can no longer be cast. Independent auditing authorities may also randomly choose uncast ballots to audit throughout the election process to provide further assurance.

\subsection{After voting}
A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand sides of each cast ballot, including its onion and vote as recorded. A voter can then verify that her vote was correctly recorded by checking that her receipt matches the information displayed on the bulletin board.

\todo{Tallying the vote}

@@

\todo{How much should we discuss here? What I said is very incomplete, but the Scantegrity II paper
doesn't say much more on the subject (instead deferring to other readings).}
